---
title: "Developing Data Products - Week 2 - Assignment"
author: "Joe M - - 26-DEC-2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### Overview 
This HTML document covers the requirements for the assignment in week 2 of the Developing Data Products course.

The requirements for this document are as follows:  
Create a web page using R Markdown that features a map created with Leaflet.

To facilitate this assignment's requirements, an interactive map is shown of the current COVID 19 status (AS of DEC 2020).  
This information is available from 21-Jan-2020 to 8-Dec-2020. 
The data set "COVID 19 Daily Updates" was acquired from Kaggle:  (https://www.kaggle.com/gpreda/coronavirus-2019ncov)

For this assignment, that information was cut down to just the US. The data was cleaned up a little. 
The running sums for each state/area was then calculated to only show a single value. The CSV file for this assignment  
has been included in the GitHub repository.

***Note***: Not all recovery numbers have been recorded. For this reason, I feel the recovery numbers are understated.


For a more streamlined view, the code for this project is given at the the bottom.

## Map of COVID cases in the US up to December 2020 map

``` {R load_libs}
library(leaflet)                                             ## Required for assignment - Map rendering
library(htmltools)                                           ## Further HTML tools for rendering
``` 


``` {R set_data}
setwd("C:/Users/Hermit/Desktop/Coursera Course/Data Science Specialization - JH/9) Developing Data Products/Week 2/DDP_Wk2_Assgn")
datamap <- read.csv(file = "covid-19-US.csv", header = TRUE, sep = ",")

    
```
     
``` {R set_MapData, message=FALSE, warning=FALSE}
df_map <- data.frame(State = datamap$State,                                 ## Create Data Frame for the COVID Data
                     Confirmed_RS = datamap$Confirmed_RS,
                     Recovered_RS = datamap$Recovered_RS,
                     Deaths_RS = datamap$Deaths_RS,
                     Latitude = datamap$Latitude,
                     Longitude = datamap$Longitude
                     )

map <- df_map %>%                                                           ## Create Map  
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=paste(df_map$State
                         , paste("<br>Confirmed Cases: ",htmlEscape(df_map$Confirmed_RS))
                         , paste("<br>Noted Recovery: ",htmlEscape(df_map$Recovered_RS))
                         , paste("<br>Noted Deaths: ",htmlEscape(df_map$Deaths_RS))
                        )
            )
```
 
```{r show_Map, message=FALSE, warning=FALSE}
map
```
   
   ----
   
### Code to create this document
Loading Libraries
``` {R load_libs, echo=TRUE, Eval=FALSE}
```   
   
Pulling in, data from the working directory 
``` {R set_data, echo=TRUE, Eval=FALSE}
```

Format Data for the Map
``` {R set_MapData, echo=TRUE, Eval=FALSE, message=FALSE, warning=FALSE}
```

Display the map
```{r show_Map, echo=TRUE, Eval=FALSE, fig.show='hide', fig.show=FALSE, results='hide'}
```







